Endogenous Politics and \\ the Design of Trade Institutions

### 2017-01-11 to-do.tex
remove to-do item about when gov't prefers to reduce e
add notes on changes from subtracting e to to-do

\section{Lobbying cost included in gov't welfare}
	\begin{itemize}
		\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
			\begin{itemize}
				\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
				\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
			\end{itemize}
		\item Subtracting $e$ gives me the kind of non-monotonicity I'd like in the graphs.
			\begin{itemize}
				\item Does it do anything to the analysis? Just shifts govt's ideal point
			\end{itemize}
		\item I think I'd like to just change to the ``$-e$'' version.
			\begin{itemize}
				\item Worries: won't match literature. Want to make analogies to GH, DGH, MRC, LT.
			\end{itemize}
	\end{itemize}

@@

\section{Lobby's optimal effort}
Need to be clear about when lobby's optimal $\tau$ is higher than gov'ts: that is, when TA would want to rein in lobby and escape clause would ruin that

>>>>

\section{Lobbying cost included in gov't welfare}
	\begin{itemize}
		\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
			\begin{itemize}
				\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
				\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
			\end{itemize}
		\item Subtracting $e$ gives me the kind of non-monotonicity I'd like in the graphs.
			\begin{itemize}
				\item Does it do anything to the analysis? Just shifts govt's ideal point
			\end{itemize}
		\item I think I'd like to just change to the ``$-e$'' version.
			\begin{itemize}
				\item Worries: won't match literature. Want to make analogies to GH, DGH, MRC, LT.
			\end{itemize}
		\item Note: there's no ``$e$'' to subtract when $\ga$ is exogenous
		\item Changes from version without $-e$:
			\begin{itemize}
				\item 3.1: $\tau_{W,e}^R$ reduced because gov't optimum is lower. $\tau^N(\ga(e))$ doesn't change because $-e$ is just a welfare shifter, isn't a function of $\tau$ is it is in menu auction setup
				\item 3.2.2: $\tau_{W,e}^R$ changes, but qualitative result doesn't change. Conjecture: more likely that this lower $\tau_{W,e}^R$ is not self-enforcing because it's lower. Should be same proof as strong vs. weak binding in JIE R$\&$R: $\pi(\tau_{W,e}^R) - e < \pi(\tau_{W,e}^R)$ is smaller, so it's harder to self-enforce. Creates a bigger gap with trade war net profit 
				\item 4.1: no change other than level of $\tau_{S,e}^F$
				\item 4.2: Side payments: need to check how transfers would change, but no obvious reasons
				\item 4.3: I was implicitly assuming something like this anyway. But I think I want to try a simple version with an export lobby.
				\item 4.4: Should write (10) more carefully because different $e$'s in three places
			\end{itemize}
	\end{itemize}

@@
